Tor's Usability for Censorship Circumvention

### 2015-12-10 paper/circumvention-experiment.tex
add link to clickable prototype
hypotheses section

\noindent {\bfseries Overview}
The Tor Browser provides a configuration interface to guide users through setting up 
their connection to the
Tor network. While people in most countries can connect to Tor using the
dialog's default settings, citizens in certain censorship environments must
make use of additional settings, such as bridges, proxies, or both. 
(Bridges are unlisted Tor relays, with pluggable transports to obfuscate traffic.
Proxies help bypass local network restrictions and are typically only
needed in restricted cases such as corporate environments.)
Our study explores how successfully this interface guides users to
correctly configuring their browser.\\

@@

Still, there remains potential for confusion, especially with the more advanced
configuration options. Bridges and proxies are not clearly defined, the
interface doesn't specify when they would need to be used, and there is limited
guidance for how to correctly choose specific values (e.g., which transport type
to use or where to find proxy settings).

\section{Hypotheses}
We expect that the average user will
struggle to connect because they lack knowledge of the technical terms and
mechanisms required for circumvention (such as pluggable transports) and cannot
obtain information not explicitly provided by the user interface (e.g., IP
addresses of non-publicly listed bridges).

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item  {\bfseries H1}: people don't know what a bridge or proxy is. > ask participants to define these terms in the survey.  
\item  {\bfseries H2}: people don't know what the difference between a bridge and a proxy is > ask if people can distinguish them. 
\item  {\bfseries H3}: people do not know when bridges or proxies are necessary > ask them this in the survey.  
\item  {\bfseries H4}: proxies cause confusion when configuring bridges. screen recording: see if people click on proxies (none of the environments require a proxy)
\item  {\bfseries H5}: people will favor familiar-sounding transports (i.e. meek-google versus meek-azure or scramblesuit) > see screen recordings, ask in survey for which transports were picked in which order and why they chose the final transport.  
\item {\bfseries H6}: (some dialogue is redundant. see opening window: "before you connect..." and bridge2 window: "you may use...") > we can try asking if people find these things useful, if they would prefer the interface without it, or if they read it.  
\end{itemize}

@@

\section{Resources}
\noindent Our online artifacts of the work done during this class, Fall 2015,
are below: 
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \href{https://github.com/lindanlee/circumvention-ux-tor}{github repo with experiment plans, code, videos, interviews, and much more}
\item \href{https://github.com/lindanlee/circumvention-ux-tor/tree/master/sessions/pre/videos}{qualitative interface evaluation videos}
\item \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/sessions/pre/participant-summaries.txt}{summaries of qualitative interface evaluation videos}
\item \href{https://github.com/lindanlee/circumvention-ux-tor/tree/master/sessions/pre/notes}{qualitative interface evaluation interview notes}
\item \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/setup/setup-environment}{experimental setup code: firewall and screen capture} 
\item \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/setup/takedown-environment}{experimental takedown code: saving files and cleanup} 
\end{itemize}

>>>>

\noindent {\bfseries Overview}
The Tor Browser provides a configuration interface to guide users through setting up 
their connection to the
Tor network. While people in most countries can connect to Tor using the
dialog's default settings, users in certain censorship environments must
make use of additional settings, such as bridges, proxies, or both. 
Our study explores how successfully this interface guides users to
correctly configuring their browser.

For context, we will give the definition of bridges, pluggable transports, and proxies. 
Keep in mind that this is the kind of information that a user might need to know to be able
to configure correctly. Note that bridges, pluggable transports, and proxies are technical 
concepts which may be unfamiliar to the average users, and that bridges and pluggable 
transports are completely Tor-specific concepts.

Bridges are unlisted Tor relays that make it possible for a user to connect
to the Tor network even if a censor blocks all publicly listed Tor relays. There used 
to be plain relays which were exactly similar to public relays, but were unlisted. However, 
censorship in countries which blocked Tor generally were motivated enough to agressively
block Tor in other ways, such as traffic analysis. For this reason, a bridge usually associated 
with a pluggable transport that circumvents deep packet inspection, transports can 
assist by obfuscating traffic or reflecting traffic through a content distribution network. 
Proxies help bypass local network restrictions and are typically only
needed in restricted cases, such as corporate environments.\\

@@

Still, there remains potential for confusion, especially with the more advanced
configuration options. Although arguably for the reason that users may not 
understand or read, bridges, pluggable transports, and  proxies are never defined 
for the user. This can lead to users confusing these terms, or not understanding
the relations between these terms. Additionally, there is limited explanation of 
what pluggable transport types to choose from if the default one fails or how to 
find proxy settings, which will be required of some users.

\section{Hypotheses}
We expected that the average user will struggle to connect because they do not understand censorship circumvention or the  censorship circumvention technologies offered by Tor. We also predict that a user will not get the feedback they need to revise their connection configuration if they fail. Specifically:

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item  {\bfseries Hypothesis 1}: users will generally not know when they need a bridge or proxy is, leading to issues such as choosing to configure a bridge or proxy when it is not necessary, or configuring bridges or proxies incorrectly. 
\item  {\bfseries Hypothesis 2}: people will not know when they need to configure or connect, since they do not understand how censorship works.   
\item  {\bfseries Hypothesis 3}: proxies will cause confusion when configuring bridges. 
\end{itemize}

We find these hypotheses to be true for our participants, although sometimes not for the reasons we expected. For instance, we believed that proxies will cause confusion when configuring bridges because participants would confuse one as the other; however, the interface redirected users to proxy configuration settings if a participant has chosen to configure a proxy, even if the source of failure was not from the proxy. Details of the experiment that has verified our hypotheses is below.

@@

\section{Resources}
\noindent Our online artifacts of the work done during this class, Fall 2015,
are below: 
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \href{https://github.com/lindanlee/circumvention-ux-tor}{github repo with experiment plans, code, videos, interviews, and much more}
\item \href {a clickable prototype of our interface redesign}{https://marvelapp.com/15a2294}
\item \href{https://github.com/lindanlee/circumvention-ux-tor/tree/master/sessions/pre/videos}{qualitative interface evaluation videos}
\item \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/sessions/pre/participant-summaries.txt}{summaries of qualitative interface evaluation videos}
\item \href{https://github.com/lindanlee/circumvention-ux-tor/tree/master/sessions/pre/notes}{qualitative interface evaluation interview notes}
\item \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/setup/setup-environment}{experimental setup code: firewall and screen capture} 
\item \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/setup/takedown-environment}{experimental takedown code: saving files and cleanup} 
\end{itemize}
